Measuring causal influence with\\ back-to-back regression: the linear case

### 2019-11-13 paper/paper.tex
small change

Note that the absence, in our model, of measurement noise over $Y$, is not restrictive. Starting from a model with measurement noise $M$, $$Y=(XE+N)F+M$$ On $Img(F)$,
we can rewrite $M = MF^{-1}F$, and we have
$$Y = (XE+N)F+M = (XE+N+MF^{-1})F = (XE+N')F$$
If $F$ has full rank, the

>>>>

Note that the absence, in our model, of measurement noise over $Y$, is not restrictive. Starting from a model with measurement noise $M$, $$Y=(XE+N)F+M$$ On $Img(F)$,
we can rewrite $M = MF^{-1}F$, and we have
$$Y = (XE+N)F+M = (XE+N+MF^{-1})F = (XE+N')F$$
If $F$ has full rank, or in $Img(F)$, the two models are equivalent.
